True versus apparent shapes of astrophysical bow shocks

### 2016-04-22 papers/Paper1/sec-application.tex
Found a relation between wind's index and \xi parameter.

This scenario can be described with the formalism of
\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
solution for the two winds interaction problem in the thin shell
approximation, in terms of a free parameter
$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
momentum ratio, which the quantities with subindex 1 corresponds to
the strongest wind, therefore $\beta<=1$.

If we apply the \CRW{} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{3}\left(1-\cos^{3/2}\theta\right) \label{eq:dotprop} \\
\dot{\Pi}_z &= \frac{1}{5}v_w \dot{M}_w^0\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}v_w\dot{M}_w^0\left(\frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta\right) \label{eq:piz}\\
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}
numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).

@@

\begin{align}
\theta_1\cot\theta_1 -1 =  \frac{8}{5}\beta E\left(\frac{\theta}{2}|2\right)\cot\theta - \frac{4}{5}\beta
\label{eq:th1th}
\end{align}

@@

\begin{align}
R_{90} &= D\tan\theta_{1,90} \\
\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{4}{5}\beta \label{eq:th190}
\end{align}
Where $\theta_{1,90}\equiv \theta_º(\frac{\pi}{2})$. Combining both equations we have:

\begin{align}
R_{90} &= D\frac{\theta_{1,90}}{1-\frac{4}{5}\beta} 
\end{align}

Expanding (\ref{eq:th190}) until 3rd order and solving for $\theta_{1,90}$:
\begin{align}
\theta_{1,90} \simeq \left(\frac{2.4\beta}{1-0.8\beta}\right)^{1/2} \\
R_{90} \simeq \left(\frac{2.4\beta}{(1-0.8\beta)^3}\right)^{1/2}
\label{eq:r90}
\end{align}

@@

>>>>

Neverthless, we should not restrict to the 0.5 index in equation (\ref{eq:nprop}). We may generalize this relation as follows:

\begin{align}
n(r_{IF},\theta) = n_0 \cos^{k}\theta
\label{eq:ngen}
\end{align}

Where $k >0$ implies that the wind's density decays towards wings, when $k<0$ the wind's density incresases towards the wings and $k=0$ implies that the wind is isotropic.

\subsection{\CRW{} Scenario}
This scenario can be described with the formalism of
\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
solution for the two winds interaction problem in the thin shell
approximation, in terms of a free parameter
$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
momentum ratio, which the quantities with subindex 1 corresponds to
the strongest wind, therefore $\beta<=1$.

If we apply the \CRW{} formalism for a more generalized photoevaporated flow with density given by (\ref{eq:ngen}), we find that the solutions for equations (8) - (11) of \CRW{} are the following:

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
\mathrm{where} & M^0_w \equiv 4\piv_w r^2_{IF} n_0 \bar{m}\\
\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w V_w I_k (\theta) \label{eq:piz}\\
I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}  we can obtain the bow shock shape $R(\theta)$. Actually, we work with two different scenarios:
% as illustred in figure (\ref{fig:r-beta}), where we show the resulting bow shock shapes for two scenarios:
$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison betwwen both solutions is shown in figure (\ref{fig:r-beta}).

@@

\begin{align}
\theta_1\cot\theta_1 -1 = 2\beta I_k(\theta) \cot\theta - \frac{2\beta}{k+2}\left(1-\cos^{k+2}\theta\right)
\label{eq:th1th}
\end{align}

@@

\begin{align}
R_{90} &= D\tan\theta_{1,90} \\
\theta_{1,90}\cot\theta_{1,90} &= 1-\frac{2\beta}{k+2} \label{eq:th190}
\end{align}
Where $\theta_{1,90}\equiv \theta_1(\frac{\pi}{2})$. Combining both equations and  introducing the parameter 
$\xi\equiv \frac{2}{k+2}$ we have:

\begin{align}
R_{90} &= D\frac{\theta_{1,90}}{1-\xi\beta} 
\end{align}

Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}) we find that:

\begin{align}
\theta_{1,90} \simeq \left(\frac{3\xi\beta}{1+\frac{1}{5}\xi\beta}\right)^{1/2} \\
\label{eq:th190sol}
\end{align}

With this, we have a solution for $B \equiv \frac{R_{90}}{R_0}$:

\begin{align}
B = \frac{\sqrt(\xi\beta)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
\label{eq:B}
\end{align}

@@

\subsection{Conic Scenario}

Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$. Continue edition from here...
